---
title: 'Tidyverse: Data Wrangling 101 - Exercises'
author: "Stijn Van de Vondel"
date: "22-9-2021"
output: 
  rmdformats::robobook:
    toc_depth: 3
---

```{r setup, include=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="120")
opts_chunk$set(#echo = FALSE,
	             #cache = TRUE,
               #prompt = FALSE,
               #tidy = TRUE,
               comment = NA#,
               #message = FALSE,
               #warning = FALSE
  )
opts_knit$set(width = 120)
```

### Exercises

Below you will find a couple of exercises to practice the `dplyr` verbs above. Often, multiple solutions exist to obtain the same answer. Feel free to use whichever tools you have at your disposal, but see to it that you *also* try with the things shown in this [5. Data manipulation with `dplyr`]!

#### Exercise 1

-   Using the `starwars` dataset, select all character columns, along with `height`. Bonus points if you can come up with multiple ways to achieve this!

-   With the selected columns, find all characters that are:

    -   taller than 150 cm and have a maximum height of 210 cm
    -   have blond or no hair colour ("none")
    -   are of the Human species
    -   not born on planets Bespin, Coruscant or Haruun Kal

```{r ex1 solution, eval = FALSE, echo = FALSE}
starwars %>% 
  select(height, where(is.character)) %>% 
  filter(height > 150, height <= 210, 
         hair_color == "blond" | hair_color == "none",
         species == "Human", 
         !homeworld %in% c("Bespin", "Coruscant", "Haruun Kal")
         )
```

#### Exercise 2
What is an alternative way of writing semi_join() (%in%)
